---
output: github_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(classdata)
library(tidyverse)
library(ggplot2)
library(rmarkdown)
library(knitr)
```

# Lab #2 Team #11 - Report:

Follow the instructions posted at https://ds202-at-isu.github.io/labs.html for the lab assignment. The work is meant to be finished during the lab time, but you have time until Monday evening to polish things.

Include your answers in this document (Rmd file). Make sure that it knits properly (into the md file). Upload both the Rmd and the md file to your repository.  

All submissions to the github repo will be automatically uploaded for grading once the due date is passed.
Submit a link to your repository on Canvas (only one submission per team) to signal to the instructors that you are done with your submission.

```
TL;DR Summary - Bhargav Yellepeddi:

The analysis of Ames property sales since 2017 shows most sales between $100K–$400K. Total living area follows a normal distribution, with outliers. A positive correlation exists between living area and sale price, though it weakens for larger properties. Missing data led to 447 rows being excluded.
```
```
TL;DR Summary - Keenan Jacobs:

In this analysis, we explore the relationship between property size (Acres) and sale price (Sale Price). We find that larger properties tend to have higher sale prices on average. However, there are some properties with large acreage that have surprisingly low sale prices, which could be due to factors such as location, property condition, or zoning regulations.
```
Keenan Jacobs - SalePrice and Acres

Bhargav Yellepeddi - SalePrice and Total Living Area Analysis:

```{r}
# Load the Ames dataset
data <- classdata::ames
```

```{r}
# View first few rows
head(data)
```

```{r}
# Inspect the structure of the dataset
str(data)
```


```{r}
unique(data[,"Sale Price"])
```


```{r}
# Histogram of SalePrice
 ggplot(data, aes(x = `Sale Price`)) +
   geom_histogram(binwidth = 20000, fill = 'blue', color = 'black') +   
   labs(title = "Distribution of Sale Prices", x = "Sale Price", y = "Count")
```


```{r}
# Summary statistics of TotalLivingArea
summary(data$`TotalLivingArea (sf)`)
```


```{r}
# Histogram of TotalLivingArea
ggplot(data, aes(x = `TotalLivingArea (sf)`)) +
  geom_histogram(binwidth = 100, fill = 'green', color = 'black') +
  labs(title = "Distribution of Ground Living Area", x = "Ground Living Area (sq ft)", y = "Count")
```


```{r}
# Scatterplot of SalePrice vs TotalLivingArea
ggplot(data, aes(x = `TotalLivingArea (sf)`, y = `Sale Price`)) +
  geom_point(color = 'purple') +
  labs(title = "Sale Price vs Ground Living Area", x = "Ground Living Area (sq ft)", y = "Sale Price")
```

Keenan Jacobs and Analysis of Acres

```{r}
summary(data$Acres)
```

The range shows a semi-wide distribution, with most properties having a small land size. Let's visualize this distribution using a histogram.

```{r}
# Histogram of Acres
ggplot(data, aes(x = Acres)) + 
  geom_histogram(binwidth = 0.1, fill = 'steelblue', color = 'black') +
  labs(title = 'Distribution of Property Size (Acres)', x = 'Acres', y = 'Frequency')

```
```{r}
# Scatterplot of Acres vs Sale Price
ggplot(data, aes(x = Acres, y = `Sale Price`)) + 
  geom_point(alpha = 0.5, color = 'darkgreen') +
  labs(title = 'Scatterplot of Property Size vs Sale Price', x = 'Acres', y = 'Sale Price ($)')

```

Here we can see there is a few huge outliers so we should probably filter them out and look again out our data as well as look at our outliers.

```{r}
# Filter properties with high Acres but low Sale Price

anomalies <- data %>% filter(Acres > 1, `Sale Price` < 50000)
filtered_data <- data %>%
  filter((Acres < 5 & `Sale Price` < 500000))

```

```{r}
# Boxplot of Anomalies by Style
ggplot(anomalies, aes(x = Style, y = `Sale Price`)) + 
  geom_boxplot(fill = 'lightgreen', color = 'darkgreen') +
  coord_flip() +  # Flip coordinates for better readability
  labs(title = 'Distribution of Sale Prices for Anomalies by Style', 
       x = 'Property Style', 
       y = 'Sale Price ($)') +
  theme_minimal()


```
```{r}
# Plotting the filtered data to confirm anomalies have been removed
ggplot(filtered_data, aes(x = Acres, y = `Sale Price`)) +
  geom_point(alpha = 0.5, color = 'darkgreen') +
  labs(title = 'Scatterplot of Property Size vs Sale Price (Filtered Data)', 
       x = 'Acres', y = 'Sale Price ($)')
```

Here we can see a few points of data looking at the anomolies and also looking at the cleaned data. From the filtered data, we cna see that there is little correlation between acre size and sales price.

